From physical principles to ???

### 2015-10-22 2015CompleteDerivation/completeDerivation.tex
Creating latex env for rationale/justification/proof

@@

\textbf{Rationale}. The claim is that deterministic and reversible evolution is necessary to be able to study a physical system. That is: the only part of a system that can be studied through reliable and reproducible experimentation or observation is the part that undergoes deterministic and reversible evolution. We can provide different arguments that point in the same direction.

@@

The second reason is that technically the assumption comes first. If we start looking for a law, we are implicitly assuming that there exists one to be found. The opposite assumption, there is no law to be found, can't really be experimentally proven exhaustively (i.e. you can only show that you have not found it among a certain class). Very often the hard part in science is finding for what system and in what conditions such assumption hold. Finding the law after that is a much simpler endeavour, and is something that is routinely done by students in their intro labs.

@@

\textbf{Justification}. The collection of all possible states from a set. The deterministic and reversible evolution maps one element in the set to one and only one element of the set.$\Box$

@@

\textbf{Justification}. A state variable associates each state to one of its values. A label, one of the possible values, can also be thought as representing all states that are identified by its value. A label range, a set of possible values, can also be thought as representing all states that are identified by those values. Abusing the notation, $\mathbbm{I}$ will represent both the set of possible values and the function, and $i$ both the possible value and the set of states.$\Box$

@@

\textbf{Rationale}. This makes a clear demarcation of what a classical object is (and conversely what a quantum object is not): it is something that can be fully described up to its infinitesimal constituents. This is clearly a \emph{simplifying} assumption, and it is instructive to understand when and why it cannot be used.

@@

The second problem is more conceptual. As we saw before, a system cannot be fully isolated from the environment. The smaller the part we study, the more it will be susceptible to fluctuations from the environment, the less we can justify the deterministic assumption, the less we are in a position to define its state. While the overall position of a ball can be considered fairly unaffected by its surrounding, the position of each small piece is going to be constantly affected by air and light scattering on its surface.

@@

\begin{defn}\label{vector space}
The state space $\mathfrak{C}$ for a infinitesimally reducible system is a vector space. Such vector is free, and admits a basis $\mathfrak{S}$ that represent the state space for the infinitesimal parts.
\end{defn}

\textbf{Justification}. We first claim that the state space $\mathfrak{C}$ is an additive monoid: there exist a law of composition $+ : \mathfrak{C} \times \mathfrak{C} \rightarrow \mathfrak{C}$ that takes two states and returns one that is the physical composition of the two. The domain and codomain match because the system is homogeneous. The law is commutative $\mathfrak{c}_1 +\mathfrak{c}_2 = \mathfrak{c}_2+\mathfrak{c}_1$ and associative $(\mathfrak{c}_1 + \mathfrak{c}_2) + \mathfrak{c}_3 = \mathfrak{c}_1 + (\mathfrak{c}_2 + \mathfrak{c}_3)$, as it does not matter in what order we compose the parts. There exist a zero element $\mathfrak{c} + 0 = \mathfrak{c}$ and it represent the state with no system.

@@

We now claim that the state space $\mathfrak{C}$ is a vector space over $\mathbbm{R}$. The abelian group $\mathfrak{C}$ can be extended with the operations defined by $A$, as each element $a \in A$ is a map $a : \mathfrak{C} \rightarrow \mathfrak{C}$. The map has the following properties: $(a_1 + a_2) \mathfrak{c} = a_1 \mathfrak{c} + a_2 \mathfrak{c}$, increasing the size of the system by the sum of two constant is the same as combining the separate increases, and $a (\mathfrak{c}_1 + \mathfrak{c}_2) = a \mathfrak{c}_1 + a \mathfrak{c}_2$, increasing the size of the total system is the same as the combination of the increased parts. $\mathfrak{C}$ is a module over $A$, which is a field and isomorphic to $\mathbbm{R}$. We can then think of $\mathfrak{C}$ as a vector space over $\mathbbm{R}$.

>>>>

\newenvironment{rationale}{\textbf{Rationale}.}{$\Box$}
\newenvironment{justification}{\textbf{Justification}.}{$\Box$}
\renewenvironment{proof}{\textbf{Proof}.}{$\Box$}

@@

\begin{rationale}
The claim is that deterministic and reversible evolution is necessary to be able to study a physical system. That is: the only part of a system that can be studied through reliable and reproducible experimentation or observation is the part that undergoes deterministic and reversible evolution. We can provide different arguments that point in the same direction.

@@

The second reason is that technically the assumption comes first. If we start looking for a law, we are implicitly assuming that there exists one to be found. The opposite assumption, there is no law to be found, can't really be experimentally proven exhaustively (i.e. you can only show that you have not found it among a certain class). Very often the hard part in science is finding for what system and in what conditions such assumption hold. Finding the law after that is a much simpler endeavour, and is something that is routinely done by students in their intro labs.
\end{rationale}

@@

\begin{justification}
The collection of all possible states from a set. The deterministic and reversible evolution maps one element in the set to one and only one element of the set.
\end{justification}

@@

\begin{justification}
A state variable associates each state to one of its values. A label, one of the possible values, can also be thought as representing all states that are identified by its value. A label range, a set of possible values, can also be thought as representing all states that are identified by those values. Abusing the notation, $\mathbbm{I}$ will represent both the set of possible values and the function, and $i$ both the possible value and the set of states.
\end{justification}

@@

\begin{rationale}
This makes a clear demarcation of what a classical object is (and conversely what a quantum object is not): it is something that can be fully described up to its infinitesimal constituents. This is clearly a \emph{simplifying} assumption, and it is instructive to understand when and why it cannot be used.

@@

The second problem is more conceptual. As we saw before, a system cannot be fully isolated from the environment. The smaller the part we study, the more it will be susceptible to fluctuations from the environment, the less we can justify the deterministic assumption, the less we are in a position to define its state. While the overall position of a ball can be considered fairly unaffected by its surrounding, the position of each small piece is going to be constantly affected by air and light scattering on its surface.
\end{rationale}

@@

\begin{defn}\label{vector space}
The state space $\mathfrak{C}$ for a infinitesimally reducible system is a vector space. It admits a basis $\mathfrak{S}$ that represents the state space for the infinitesimal parts.
\end{defn}

\begin{justification}
We first claim that the state space $\mathfrak{C}$ is an additive monoid: there exist a law of composition $+ : \mathfrak{C} \times \mathfrak{C} \rightarrow \mathfrak{C}$ that takes two states and returns one that is the physical composition of the two. The domain and codomain match because the system is homogeneous. The law is commutative $\mathfrak{c}_1 +\mathfrak{c}_2 = \mathfrak{c}_2+\mathfrak{c}_1$ and associative $(\mathfrak{c}_1 + \mathfrak{c}_2) + \mathfrak{c}_3 = \mathfrak{c}_1 + (\mathfrak{c}_2 + \mathfrak{c}_3)$, as it does not matter in what order we compose the parts. There exist a zero element $\mathfrak{c} + 0 = \mathfrak{c}$ and it represent the state with no system.

@@

We now claim that the state space $\mathfrak{C}$ is a vector space over $\mathbbm{R}$. The abelian group $\mathfrak{C}$ can be extended with the operations defined by $A$, as each element $a \in A$ is a map $a : \mathfrak{C} \rightarrow \mathfrak{C}$. The map has the following properties: $(a_1 + a_2) \mathfrak{c} = a_1 \mathfrak{c} + a_2 \mathfrak{c}$, increasing the size of the system by the sum of two constant is the same as combining the separate increases, and $a (\mathfrak{c}_1 + \mathfrak{c}_2) = a \mathfrak{c}_1 + a \mathfrak{c}_2$, increasing the size of the total system is the same as the combination of the increased parts. $\mathfrak{C}$ is a module over $A$, which is a field and isomorphic to $\mathbbm{R}$. We can then think of $\mathfrak{C}$ as a vector space over $\mathbbm{R}$.
\end{justification}
